An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-10-28 EconGrowth.Rnw
Removed ylim adjustments.

<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2.5)
@

@@

<<CESq_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
@

<<CESq_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
@

@@

<<CESx_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(kl)e") + ylim(0, 2.5)
@

<<CESx_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(kl)e") + ylim(0, 2.5)
@

@@

<<CESu_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(kl)e") + ylim(0, 2.5)
@

<<CESu_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(kl)e") + ylim(0, 2.5)
@

@@

<<CESq_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k") + ylim(0, 2.5)
@

<<CESq_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k") + ylim(0, 2.5)
@

@@

<<CESx_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(le)k") + ylim(0, 2.5)
@

<<CESx_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(le)k") + ylim(0, 2.5)
@

@@

<<CESu_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(le)k") + ylim(0, 2.5)
@

<<CESu_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(le)k") + ylim(0, 2.5)
@

@@

<<CESq_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
@

<<CESq_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
@

@@

<<CESx_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(ek)l") + ylim(0, 2.5)
@

<<CESx_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(ek)l") + ylim(0, 2.5)
@

@@

<<CESu_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(ek)l") + ylim(0, 2.5)
@

<<CESu_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(ek)l") + ylim(0, 2.5)
@

@@

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q") + ylim(-20, 10)
@

<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
linexResamplePlot(energyType="X") + ylim(-20, 10)
@

>>>>

<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType=NA)
@

@@

<<CESq_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e")
@

<<CESq_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e")
@

@@

<<CESx_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(kl)e")
@

<<CESx_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(kl)e")
@

@@

<<CESu_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(kl)e")
@

<<CESu_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(kl)e")
@

@@

<<CESq_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k")
@

<<CESq_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k")
@

@@

<<CESx_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(le)k")
@

<<CESx_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(le)k")
@

@@

<<CESu_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(le)k")
@

<<CESu_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(le)k")
@

@@

<<CESq_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l")
@

<<CESq_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l")
@

@@

<<CESx_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="X", nest="(ek)l")
@

<<CESx_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="X", nest="(ek)l")
@

@@

<<CESu_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
cesResamplePlotSigma_1Delta_1(energyType="U", nest="(ek)l")
@

<<CESu_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
cesResamplePlotSigmaDelta(energyType="U", nest="(ek)l")
@

@@

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q")
@

<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
linexResamplePlot(energyType="X")
@
